Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-12-29 manuscript.Rmd
Update WCRQA results

For social cohesion and count of all events, there was a consistent period of
above-chance RR from the 2nd--12th and 44th--50th window. DET was largely above chance
from the 47th to the 52nd window, with some exceptions (Figure
\@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of positive events, we saw a downward trend in RR
as the window advances throughout the sample. Interestingly, we see largely
above-chance RR until the 18th window, with an exception for window 17. A peak also appeared for the 40th--42nd windows. DET was intermittently at or above chance for the 8th--14th and 54th--62nd windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of negative events, RR stayed above or almost
above chance from the 4th--7th and 46th--49th windows and was below chance for extended period from the 56th--62nd window. DET bottomed out at zero for the 15th--23rd and 34th--39th windows. The metric was above or nearly above chance only toward the end of the time series, in the 47th--54th and 62nd windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

@@

For social cohesion and count of all events, there was a consistent period of
above- or nearly above-chance DET from the 2nd--18th and 44th--52nd windows. DET
also showed above- or nearly above-chance values in windows 7--11 and 59--62 (Figure
\@ref(fig:plot-wcrqa-source-targ-all)).

For social cohesion and count of positive events, there was a downward trend in
RR as the window moved, with above-chance values in the first 23 windows
and the 57th--62nd windows. DET stayed largely within chance, with the exception
of windows 1 and 4 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).

For social cohesion and negative events, RR was above chance for the 4th--6th and 46th--49th windows and below chance for the 56th--62nd windows. DET showed an upward trend as the windows moved. It bottomed out to zero for the 15th--23rd and 34th--39th windows, and was only above change for the 47th--54th and 62nd windows. (Figure
\@ref(fig:plot-wcrqa-source-targ-all)).

>>>>

For social cohesion and count of all events, there was a consistent period of
at or above-chance RR from the 3rd--12th and 44th--50th window. DET was largely above chance
from the 47th to the 54th window, with some exceptions (Figure
\@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of positive events, we saw a downward trend in RR
as the window advances throughout the sample. Interestingly, we see largely
above-chance RR until the 16th window, with an exception for window 1. A peak also appeared for the 40th--42nd windows. DET was intermittently at or above chance for the 8th--14th and 54th--62nd windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of negative events, RR stayed above or almost
above chance from the 5th--6th and 46th--49th windows and was below chance for an extended period from the 56th--62nd window. DET bottomed out at zero for the 15th--23rd windows. The metric was above or nearly above chance only toward the end of the time series, in the 47th--54th and 62nd windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

@@

For social cohesion and count of all events, there was a consistent period of
above- or nearly above-chance RR in the first 23 windows and the 44th--52nd windows. RR was consistently below chance for the 29th--39th windows. DET showed above- or nearly above-chance values in windows 7--11 and 59--62 (Figure
\@ref(fig:plot-wcrqa-source-targ-all)).

For social cohesion and count of positive events, there was a downward trend in
RR as the window moved, with above- or nearly above-chance values in the first 23 windows
and the 57th--62nd windows. RRR was largely below-chance for the 30th--38th windows. DET stayed largely within chance with intermittent bottoming-out to a value of 0 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).

For social cohesion and negative events, RR was above chance for the 7th window and below chance for the 15th--19th windows, intermittently below chance beetween the 25th--39th windows, and below chance for the 51st--62nd windows. DET showed a downward trend as the windows moved, with no abovee-chance values. It bottomed out to zero for the 15th--20th and 24th-27th windows, intermittently bottomed out for the 34th--45th windows, and consistently bottomed out for the 52nd--62nd windows. (Figure
\@ref(fig:plot-wcrqa-source-targ-all)).
